%----------------------------------------------------------------------------------------
%    SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Relevant Experience}

%----------------------------------------------------------------------------------------
%    SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%%----------------------------------------=--------

\cventry
{Co-director} % Job title
{Quansight Labs} % Organization
{Manchester, UK} % Location
{January 2021-present } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item{Defining data science and analytics initiatives, and key performance indicators, enabling the company and teams to validate and deliver strategic goals.}
    \item{Working with clients to lead transitions to data-driven decision making across business functions, via coaching, OKR definition, and advising on tools and methodologies.}
    \item {Guiding and supporting a diverse team of over 20 Software and DevOps engineers, UX Designers, Developer Advocates, Data Scientists and managers.}
    \item {Grew the technical team to a size of over 100 individuals while improving our EDI (Equality, Diversity and Inclusion) and HR practices.}
    \item {Cultivate and implement a culture of inclusion, mentorship and collaboration across the organisation.}
    \item {Engaged in a variety of leadership roles, including managing the company's diversity and inclusion initiatives and leading the company's data open-source initiative.}
    \item {Provided technical leadership on critical projects involving Full Stack data science and MLOps.}
    \item {Won and managed substantial grants with NASA and CZI to support and strengthen the scientific computing open-source ecosystem.}
    \item {Led internal and client's teams to work on and deliver a variety of projects, including data science platforms and applied Machine Learning projects across multiple industries.}
    \item{Managed, grew, and motivated a group of data scientists and open-source developers across multiple timezones.}
    \item {Mentored the professional development of each direct report through personal and performance management}
    \item {Developed strong cross-functional partnerships across Quansight and with external stakeholders.}
    \item {Responsible for the team's technical strategy and roadmap – creating success metrics in close collaboration with other Engineering and Product Managers.}
    \item {Facilitated open communication and discussion between stakeholders, acting as a single point of contact by developing, maintaining and working to stakeholder engagement strategies and plans.}
    \item {Sought to fully address client needs, enhancing the capabilities and effectiveness of client personnel, by ensuring that proposed solutions are properly understood and appropriately exploited.}
    \item {Balance multiple projects and priorities to deliver maximum impact to the organisation and the open-source communities we worked with.}
\end{cvitems}
}
%%----------------------------------------=--------
%%----------------------------------------=--------

\cventry
{Sr. Developer Advocate} % Job title
{Microsoft} % Organization
{Manchester, UK} % Location
{March 2019-December 2020 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Technical lead for the Academic developer advocacy team. Overseeing multiple projects simultaneously and leading teams of developer advocates, engineers, researchers,  and project managers.}
\item {Defined strategies to better serve and collaborate with the scientific community. Before joining the team, there was no formal engagement with the Research software engineering or scientific computing community. These strategies have to lead to the development of research, specific content and documentation. Research partnerships and deeper collaboration in open data and open science projects.}
\item {Co-developed the Python advocacy strategy focusing on the Education, Scientific Computing and Data Science groups/community.}
\item{Project planning and resources allocations for scientific computing and major research projects within Microsoft and with global universities, libraries, and research institutes. }
\item {Work with engineering teams to identify gaps in a range of products, integrate community feedback and work project road mapping.}
\item {Develop high-quality content (tutorials, blogs, videos, streams, etc.) for the developer community.}
\item {Organised community-oriented events (meetups, sprints, hackathons) and international conferences (JupyterCon, RSE conference, SciPy, PyCon UK, Pyjamas, ML summit, among others).}
\end{cvitems}
}

%%------------------------------------------------

\cventry
{Data/research engineer} % Job title
{Hello Soda } % Organization
{Manchester, UK} % Location
{July 2018-February 2019 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Planned, implemented and supervised the further improvements of a robust data platform that allows for continuous delivery, monitoring, and logging of machine learning and natural language processing models (over 60 models with incoming data from customers in Europe, Asia, USA, and Latin America).}
\item{Developed internal policies regarding data and software best practices, documentation, and model deployment.}
\item{Managed engineering and data science team members: ensuring that the projects were seen to completion and deadlines were met. Worked with the team and individuals to set personal development and business goals every quarter. Led sprints planning, retrospectives and daily stand-ups.}
\item{Introduced fortnightly documentation sprints and show and tells for the tech team (data, infrastructure, engineering) as well as a reading club for folks to share novel articles and discuss techniques and tools.} 
\item{Developed tools and infrastructure to scale, support and improve the data team tasks, from data extraction to model development, training, and optimisation, to taking models into production.}
\item{Leveraged the use of tools such as Elasticsearch, Airflow, Pachyderm, Docker, Rstudio, Jupyter, cloud solutions, and Kubernetes within the development areas of the business.}
\item{Drove the adoption of tools and processes to improve our data models reproducibility, provenance (lineage), and sustainability. Leading to a 30\% reduction in incidents associated with drifting, model staleness and performance.}
\item {Reduced the time-to-production from an average of 14 days to a maximum of 4 days by adopting MLOps principles and automation.}
\end{cvitems}
}

%%------------------------------------------------

\cventry
{Data and reproducibility consultant } % Job title
{Freelance / consultant } % Organization
{Manchester,  UK} % Location
{Nov 2016 - present } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Consulted start-ups and researchers on reproducible data analysis workflows, open data, data modelling and aided them to develop strategies to satisfy their data engineering needs. Reducing in most of the cases the computational times and optimised their data-intensive workflows.}
\item {Created and presented executive dashboards to show data insights using R Shiny apps, Plotly, and d3.js}
\item {Implementation and scaling of data pipelines, from ETL to model deployment, monitoring and task scheduling.}
\item{Worked with industry customers to design and implement MLOPs systems.}
\item {Individual management coaching.}
\item {Defined and implemented data science and MLOps intitiatives as well as OKRs for diverse teams.}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Research software engineer  / Machine learning team member } % Job title
{The University of Sheffield } % Organisation
{Sheffield, UK} % Location
{Nov 2016 - June 2018 } % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Main contributor to the European funded projects OpenDreamkit as well as to several open-source projects, such as project Jupyter, GPS for Gaussian Processes, RopenSci, among others aimed at applied Data Science.}
% \item {Used RESTful web design using Flask, Jinja2, JQuery, JS and Django for the development of multiple web apps.}
\item {Developed numerous data analysis pipelines, from wrangling to prediction and results dissemination, for research projects in Linguistics (Natural Language Processing), Bioinformatics (Classification and regression), Materials science (regression), and Geography (geolocation data analysis) using R and Python.}
\item { Implemented the use of third parties API's and web scraping to collect raw data for posterior analysis and modelling.}
\item {Trained and supervised junior colleagues and students, with a particular focus on reproducible workflows, software development best practices, High-Performance Computing, and open-source projects.}
\item {Worked in policy creation at both a national and international level as a member of the UK Research Software Engineering and NUMFocus Diversity and Inclusion in Scientific Computing committees.}
\item {Developed interactive dashboards and data visualisations using d3.js, Shiny, Bokeh, and Plotly to disseminate project findings.}
\item{Developed tools to support reproducible research and literate programming.}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Consultancy fellow}
{NHS, Manchester business school}
{Manchester, UK}
{February - October 2016}
{
\begin{cvitems}
\item {Liaised with multiple stakeholders, from executive directors to patients within the NHS identify and define organisational priorities.}
\item  {Led data collection and statistical analyses.}
\item  {Improved the efficiency of Emergency services by a 20\% in terms of patient waiting times and diagnosis times.}
\item{Developed a framework for specialist hospitals within the Greater Manchester area to improve the sharing of institutional knowledge, to improve the efficiency of communication, and to eliminate 50\% of unnecessary meetings.}
\end{cvitems}
}


%------------------------------------------------   

%\cventry
%{ Foundation year mentor /  Teaching assistant}
%{The University of Manchester}
%{Manchester, UK}
%{January 2013 - December 2016}
%{
%\begin{cvitems}
%\item {Foundation tutor: lead teams of 5-6 people across the full length of the research projects:
%from the literature review, to experimental design, to results reporting.}
%\item { Developed classes materials and delivered lectures/tutorials on MATLAB, Finite Element
%Analysis, Data analysis, Mechanical testing, statistics.}
%\end{cvitems}
%}


%------------------------------------------------

%\cventry 
%{College teacher}
%{ULA}
%{Mexico City, Mexico}
%{2012-2013}
%{}

%------------------------------------------------
\cventry
{Engineering intern}
{University of Southern California, MEMS}
{California, USA}
{2011}
{
\begin{cvitems}
\item {Performed real-time data collection and analysis for implantable drug delivery devices, leading to a 20\% increase in dose tracking and fault detection accuracy.}
\item {Architected and implemented analytics and visualisation components for a device data analysis platform to predict potential hardware failures.}
\end{cvitems}
}
%------------------------------------------------

%\cventry
%{College and junior university teacher}
%{IPN}
%{Mexico City, Mexico}
%{2005-2013}
%{}

\end{cventries}∑